%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {DarwinAI} % Organization
    {Waterloo, ON} % Location
    {Nov. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected the inference component of the inspection system, serving AI models for defect detection using NVIDIA Triton, resulting in functional system with hot-swappable models.}
        \item {Contributed system-wide features spanning back-end (FastAPI/Express) and front-end systems (Angular), enhancing the functionality of the system.}
        \item {Successfully established a software interface connecting cameras with the visual inspection system leveraging Vimba/Sapera LT.}
        \item {Contributed to packaging and installation scripts for each component of the system resulting and faster and more simple installation process.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Back-end Developer} % Job title
    {DarwinAI} % Organization
    {Waterloo, ON} % Location
    {Nov. 2018 - Nov. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed to the development of a deep learning models optimization platform utilizing Tensorflow 1 and Python.}
        \item {Spearheaded a memory optimization initiative, effectively eliminating memory leaks from 3rd party frameworks  by strategically refactoring application components to leverage OS processes, resulting in the product being able to run for weeks vs days.}
        \item {Developed and implemented simple deep learning models, including ResNet and Simpnet, to expand the local model collection for verification purposes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Engineer} % Job title
    {DarwinAI} % Organization
    {Waterloo, ON} % Location
    {Apr. 2018 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led implementation of the initial infrastructure for CI pipelines using Jenkins, Bitbucket and AWS, improving code quality.}
        \item {Developed automated test suites for the product, conducted manual testing to verify newly added features.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Ericsson} % Organization
    {Ottawa, ON} % Location
    {Jun. 2017 - Apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed to the collection of automated test suites for a high-performance 5G system in C.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Embedded Engineering Intern} % Job title
    {NVIDIA} % Organization
    {Santa Clara, CA} % Location
    {Jul. 2014 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Li-ion batter charger logic on a Cortex M0 bare-bone micro-controller in C, with successful performance verification using lab equipment.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
